### 2015-03-23 Paper1Editted/paper1Beditted.tex

\subsection*{Human Intent Trajectories}
Extraction of intent from human point-to-point reaching revealed straight-line movement that persisted for hundreds of milliseconds after the onset of disturbing forces (Figure 3A). If intent can change following disturbance, it can only do so after some period of time due to processing and communication delays in the sensorimotor system that produces new motor commands. We hypothesized that intent should not diverge from the undisturbed intent path even if the actual hand was disturbed within this window of delay. In both pulse timing conditions, the intended trajectory remained straight towards the target, even though the actual hand was dramatically deflected, supporting our hypothesis and the approach.

These results suggested a reproducible approach for inspecting how individuals might alter their intent in response to disturbances. Actual hand paths could no longer be explained ($p=0.05$) by deviation in undisturbed movement within 145 milliseconds after the onset of disturbance. Despite the disturbance, three subjects' intents did not depart significantly from baseline. The remaining five subjects' intents deviated between 150 and 255 milliseconds after the hand deviated (Figure 3B). When disturbances occurred early in reaching, intent showed some signs of correction mid-reach. When disturbances occurred later, the intent continued to the target, but interestingly, it then corrected (Figure 3A). Intention showed systematic deflections that counteracted the direction of disturbance beginning about 200 milliseconds after the onset of the force disturbance; however, this counteraction did not immediately depart from the range of undisturbed movements (Figure 3B, orange region). This counteraction is consistent with both change of intent and stiffening in response to the disturbance.

@@

Interestingly, the formulation leads to some implications on the expected behavior of this moving equilibration. Even if the muscle equilibrium jumped abruptly, this would be insufficient to move the intended trajectory abruptly due to the presence of the mass term in the intention formulation -- reaching intent cannot jump abruptly. The intent trajectories certainly follow this pattern, smoothly responding to disturbances at a latency of about 200 milliseconds. While this work examines the tendencies of the onset of change, statistical testing cannot be used to detect the absence of change in an individual movement. Still, Figure 3 shows reaches that are more compatible with intermittent control than with continuous optimal feedback control. In classic optimal control, the system is always updating intent in response to error \cite{todorov2002optimal}. While most of our subjects displayed a latent response consistent with sensory feedback latencies \cite{pruszynski2012optimal}, three subjects showed no detectable response. The absence of response to a large force disturbance seems inconsistent with optimal feedback control framework and is instead consistent with adherence to a trajectory planned before the disturbance. Control that is intermittent \cite{gawthrop2011intermittent} with limited opportunities to change intent can explain both change and lack thereof. It remains to be seen if and how change in intent might be triggered.

>>>>

\subsection*{Human Intent Trajectories}
Extraction of intent from human point-to-point reaching revealed straight-line movement that persisted for hundreds of milliseconds after the onset of disturbing forces (Figure 3A). If intent can change following disturbance, it can only do so after some period of time due to processing and communication delays in the sensorimotor system that produces new motor commands. We hypothesized that intent should not diverge from the undisturbed intent path even if the actual hand was disturbed within this window of delay. In both pulse timing conditions, the intended trajectory remained straight towards the target in excess of 120 milliseconds ($p<0.001$), even though the actual hand was dramatically deflected, supporting our hypothesis and the approach.

These results suggested a reproducible approach for inspecting how individuals might alter their intent in response to disturbances. Actual hand paths could no longer be explained ($p=0.05$) by deviation in undisturbed movement within 145 milliseconds after the onset of disturbance. Despite the disturbance, three subjects' intents did not depart significantly from baseline (Figure 3, left portion). The remaining five subjects' intents deviated between 150 and 255 milliseconds after the hand deviated (Figure 3, right portion). When disturbances occurred early in reaching, intent showed some signs of correction mid-reach. When disturbances occurred later, the intent continued to the target, but interestingly, it then corrected. Intention showed systematic deflections that counteracted the direction of disturbance beginning about 200 milliseconds after the onset of the force disturbance; however, this counteraction did not immediately depart from the range of undisturbed movements (Figure 3B, orange region). This counteraction is consistent with both change of intent and stiffening in response to the disturbance.

@@

Interestingly, the formulation leads to some implications on the expected behavior of this moving equilibration. Even if the muscle equilibrium jumped abruptly, this would be insufficient to move the intended trajectory abruptly due to the presence of the mass term in the intention formulation -- reaching intent cannot jump abruptly. The intent trajectories certainly follow this pattern, smoothly responding to disturbances at a latency of about 200 milliseconds. While this work examines the tendencies of the onset of change, statistical testing cannot be used to detect the absence of change in an individual movement. Still, Figure 3 shows reaches that are more compatible with intermittent control than with continuous optimal feedback control. In classic optimal control, the system is always updating intent in response to error \cite{todorov2002optimal}. While most of our subjects displayed a latent response consistent with sensory feedback latencies \cite{pruszynski2012optimal}, three subjects showed no detectable response. The absence of response to a large force disturbance is instead consistent with adherence to a trajectory planned before the disturbance. Control that is intermittent \cite{gawthrop2011intermittent} with limited opportunities to change intent can explain both change and lack thereof. It remains to be seen if and how change in intent might be triggered.
